ML-Runner: A Scalable Cloud System for Machine \& Distributed Learning

### 2018-05-11 Paper.tex
w multicols
err commit

\maketitle
\setlength{\columnsep}{20pt}
%\begin{multicols}{2}

% -------------- INTRODUCTION --------------
% ------------------------------------------
\section{Introduction}\label{sec:introduction}
In short, the Ethereum network provides us with a framework for creating distributed application that can act as a trustless, uncensorable digital content store.

@@

%\end{multicols}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

%\begin{multicols}{2}
% -------------- FUTURE DIRECTIONS --------------
% -----------------------------------------------
\section{Future Directions} \label{ch:future}
In our application we used AWS Elastic Beanstalk to run the containerized experiments for each configuration, since this is what we were familiar with.
It may be preferable to use AWS Elastic Container Service instead, since we already package the code in docker containers, though due to time constraints we did not get a chance to investigate this option.

@@

%\end{multicols}
\bibliographystyle{plainnat}
\bibliography{Biblio}

>>>>

\maketitle
\setlength{\columnsep}{20pt}
\begin{multicols}{2}

% -------------- INTRODUCTION --------------
% ------------------------------------------
\section{Introduction}\label{sec:introduction}
Machine learning models typically involve some number of configurable hyperparameters which we call $\lambda = \{ \lambda_i \}$.
Among the valid op

@@

\end{multicols}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

\begin{multicols}{2}
% -------------- FUTURE DIRECTIONS --------------
% -----------------------------------------------
\section{Future Directions} \label{ch:future}
In our application we used AWS Elastic Beanstalk to run the containerized experiments for each configuration, since this is what we were familiar with.
It may be preferable to use AWS Elastic Container Service instead, since we already package the code in docker containers, though due to time constraints we did not get a chance to investigate this option.

@@

\end{multicols}
\bibliographystyle{plainnat}
\bibliography{Biblio}
